Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
specify seed=34 within bootMer function throughout code.

  if(is.null(bootstraps) == FALSE){
    set.seed(34) # make sure results are reproducible
    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

  if(is.null(bootstraps) == FALSE){
    set.seed(34) # make sure results are reproducible
    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

@@

```{r Bootstrap food-web model, cache=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

@@

```{r Bootstrap linear food-web model, cache=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

@@

```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

@@

```{r Bootstrap linear egg vs. larval model, cache=TRUE}
boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

@@

```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

@@

```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
```

>>>>

  if(is.null(bootstraps) == FALSE){

    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32, seed=34)

@@

  if(is.null(bootstraps) == FALSE){

    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32, seed=34)

@@

```{r Bootstrap food-web model, cache=TRUE}
boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bootstrap linear food-web model, cache=TRUE}
boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bootstrap linear egg vs. larval model, cache=TRUE}
boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```

@@

```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
```
